[Re] On the coexistence of specialists and generalists

### 2017-10-16 article/Poisot-2017.tex
PDF compiled

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Timothée Poisot,
  },
            pdftitle=
{
[Re] On the coexistence of specialists and generalists
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\begin{equation}
\mathbf{K} = \begin{bmatrix}
  K_1 & aK_1 \\
  a_K2 & K_2 \\
  bK_1 & b_K2
\end{bmatrix} \,.
\end{equation}

@@

\begin{equation}
D_{l1} = \frac{\sum_{i\in l,m,m}p_iN_i}{K_{l1}}
\end{equation}

@@

\begin{equation}
D_{l2} = \frac{\sum_{i\in l,m,m}(1-p_i)N_i}{K_{l1}} \,.
\end{equation}

@@

@@

Original sources were not available, and no attempts were made to
contact the authors. For some non-stochastic situations, it is possible
to calculate expected values by hand. The original manuscript does
provide some of these values, and they were used to test this
implementation. Figure 2A and 2B in the original manuscript provide a
good diagnostic value, as they are based on non-stochastic situations.
In \textcite{fig:02},

@@

Results should be compared with original results and you have to explain
why you think they are the same or why they may differ (qualitative
result vs quantitative result). Note that it is not necessary to redo
all the original analysis of the results.

@@

Conclusion, at the very minimum, should indicate very clearly if you
were able to replicate original results. If it was not possible but you
found the reason why (error in the original results), you should exlain
it.

\begin{longtable}[]{@{}llllll@{}}
\caption{Table caption \{\#tbl:table\}}\tabularnewline
\toprule
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 1\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 2\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 1\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 2\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\midrule
\endhead
cell1 row1 & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 &
cell6 row 1\tabularnewline
cell1 row2 & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 &
cell6 row 2\tabularnewline
cell1 row3 & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 &
cell6 row 3\tabularnewline
\bottomrule
\end{longtable}

A reference to table \textcite{tbl:table}. A reference to figure
\textcite{fig:logo}. A reference to equation \textcite{eq:1}. A
reference to citation \textcite{markdown}.

\begin{figure}
\centering
\includegraphics{rescience-logo.pdf}
\caption{Figure caption}\label{fig:logo}
\end{figure}

\[ A = \sqrt{\frac{B}{C}} \] \{\#eq:1\}

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Timothée Poisot,
  },
            pdftitle=
{
[Re] On the coexistence of specialists and generalists
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\begin{equation}
\mathbf{K} = \begin{bmatrix}
  K_1 & aK_1 \\
  aK_2 & K_2 \\
  bK_1 & b_K2
\end{bmatrix} \,.
\end{equation}

@@

\begin{equation}
D_{l1} = \frac{\sum_{i\in l,m,n}p_iN_i}{K_{l1}}
\end{equation}

@@

\begin{equation}
D_{l2} = \frac{\sum_{i\in l,m,n}(1-p_i)N_i}{K_{l1}} \,.
\end{equation}

@@

\hypertarget{tbl:prm}{}
\begin{longtable}[]{@{}llr@{}}
\caption{\label{tbl:prm}Default parameters. Unless otherwise specified,
these parameters have been used for all figures. }\tabularnewline
\toprule
Parameter & Meaning & Default value\tabularnewline
\midrule
\endfirsthead
\toprule
Parameter & Meaning & Default value\tabularnewline
\midrule
\endhead
\(r\) & \emph{per capita} growth rate & \(1.3\)\tabularnewline
\(a\) & fitness cost of specialism & \(0.1\)\tabularnewline
\(b\) & fitness cost of generalism & \(0.9\)\tabularnewline
\(K_1\) & range of habitat quality (1) & \([200,200]\)\tabularnewline
\(K_2\) & range of habitat quality (1) & \([100,100]\)\tabularnewline
\(g\) & proportion picking a random habitat & \(0.0\)\tabularnewline
\bottomrule
\end{longtable}

@@

Original sources were not available, and no attempts were made to
contact the authors. For some non-stochastic situations, it is possible
to calculate expected values by hand. The original manuscript does
provide some of these values, and they were used to test this
implementation. All default parameter values are given in
~\ref{tbl:prm}. In all figures, circles represent the generalist, upper
and lower triangles represent the specialists of habitats 1 and 2
(respectively), and a diamond is used when both specialists have the
same behaviour.

Figure 2A and 2B in the original manuscript provide a good diagnostic
value, as they are based on non-stochastic situations. These are
reproduced in ~\ref{fig:02}. As in the original simulations, the
generalist alone overshoots its carrying capacity at \(t=5\), and the
stabilizes at a value of \(N_3^\star = 270\). Note also that
\(p_3 = 2/3\) , which represents the ratio of habitat qualities. When
adding specialists at initial densities of \(N_1 = N_2 = 1\), we observe
(i) that the preference of the generalist shifts towards habitat 1 to
avoid competition in the smallest habitat, and (ii) the density of the
specialist of habitat 2 stabilizes as soon as the generalist abandons
habitat 2 (at \(t \approx 35\)).

@@

In ~\ref{fig:03}, this implementation gives the same qualitative results
as the original article. There are small quantitative differences in
output, which are in my opinion explained by the initial population
densities (which are not given in the original article). Absent
variation in habitat quality, generalists cannot persist, and the
specialists both reach \(N^\star = \bar K\). There is a value of
variation for which the densities of specialists and generalists are
equal (about 110 for tied variations, and 130 for independent
variations).

\begin{figure}
\centering
\includegraphics{figure03.pdf}
\caption{Consequences of increasing the range of variation of both
\(K_1\) and \(K_2\). Dashed lines represent independent variation, and
solid lines tied variations, as in the original article.}\label{fig:03}
\end{figure}

In ~\ref{fig:04}, the same qualitative result (generalists increase in
abundance when one habitat becomes larger). The quantitative differences
can, again, be explained by changes in the initial population densities.
Finally, the results in ~\ref{fig:05} and ~\ref{fig:06} can also be
replicated.

\begin{figure}
\centering
\includegraphics{figure04.pdf}
\caption{Consequences of increasing the range of variation of both
\(K_1\) and \(K_2\). Dashed lines represent independent variation, and
solid lines tied variations, as in the original article.}\label{fig:04}
\end{figure}

\begin{figure}
\centering
\includegraphics{figure05.pdf}
\caption{Consequences of increasing the range of variation of both
\(K_1\) and \(K_2\). Dashed lines represent independent variation, and
solid lines tied variations, as in the original article.}\label{fig:05}
\end{figure}

\begin{figure}
\centering
\includegraphics{figure06.pdf}
\caption{Consequences of increasing the range of variation of both
\(K_1\) and \(K_2\). Dashed lines represent independent variation, and
solid lines tied variations, as in the original article.}\label{fig:06}
\end{figure}

@@

I believe that this implementation faithfully reproduces the results of
\textcite{wils94csg}. A single run of the model (using 100 generations
as in the original article) completes in
\(\approx 5\times 10^{-3} \text{s}\). This makes this implementation
usable for teaching, as it is not time consuming to generate results. As
an example, I merged the output of ~\ref{fig:03} and ~\ref{fig:05}, to
generate the response of Shannon's evenness (which measures the extent
to which all species have the same density) to changes in the rate of
variation \emph{and} generalist ability. The results are presented in
~\ref{fig:surf}.

\begin{figure}
\centering
\includegraphics{figureSurf.pdf}
\caption{Response of the model to changing the ability of the generalist
\emph{and} the range of variation. While the response to environmental
change is bell-shaped when generalists are competitive (\(g\) close to
unity), it becomes monotonously decreasing for generalists with lower
competitive ability (\(g\) close to \(a\)).}\label{fig:surf}
\end{figure}
